### 2023-11-15 conclusion.tex
Updates from Overleaf
Update artifact ref and data availability statement

@@

\section*{Data Availability Statement}
An artifact \cite{zhao2023} containing the Agda mechanization and the implementation of Hazel
including type hole inference is available.

>>>>

\section*{Data Availability Statement}
An artifact \cite{zhao2023} containing the complete formalization of the marked lambda calculus and the extensions described, the Agda mechanization, and the implementation of Hazel including type hole inference is available.
Up-to-date versions of the formalism and mechanization may be found at \url{https://github.com/hazelgrove/error-localization-agda}.
Hazel is being actively developed---more information is available at \url{https://hazel.org}, and the Hazel source code is maintained at \url{https://github.com/hazelgrove/hazel}.

@@
